Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-05-24 analysis/paper/supplement.Rmd
Draft to coauthors.

# (APPENDIX) Supplementary Material for National demographic-disturbance relationships and local monitoring both reduce uncertainty in projections of boreal caribou population viability: tools to support monitoring decisions {-}

>>>>

# (APPENDIX) Supplementary Material for Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions {-}
